---
title: "SKC_MSDS6306_Casestudy01"
author: "sabitri kc"
date: "June 30, 2017"
output: 
  html_document:
   keep_md: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The purpose of this presentation is to provide the analysis of two data sets called "Beers" and "Breweries".Beers dataset contains a list of 2410 US craft beers and Breweries dataset contains 558 US breweries.The datasets descriptions are as follows:

####Beers.csv:
* Name: Name of the beer. 
* Beer ID: Unique identiﬁer of the beer. 
* ABV: Alcohol by volume of the beer. 
* IBU: International Bitterness Units of the beer. 
* Brewery ID: Brewery id associated with the beer. 
* Style: Style of the beer. Ounces: Ounces of beer.

####Breweries.csv: 
* Brew ID: Unique identiﬁer of the brewery.
* Name: Name of the brewery. 
* City: City where the brewery is located. 
* State: State where the brewery is located.

**SessionInfo:**
R version 3.4.0 (2017-04-21)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows >= 8 x64 (build 9200)

##Setup Requirement
```{r}
# install and load following packages:
library(dplyr)
library(ggplot2)

```
```{r}
# Find out the working directory
setwd("C:/DOING DATA SCIENCE 6306/Unit 7/CaseStudy_01/Data")
getwd()

# Load the data from csv file and stored in data frame
beerdata <- read.csv("Beers.csv" , TRUE, ",")
 class(beerdata)
 dim(beerdata)
 head(beerdata)

breweriesdata <- read.csv("Breweries.csv" , TRUE, ",")
class(breweriesdata)
dim(breweriesdata)
head(breweriesdata)
```
## Analysis of data:
```{r}
#Total number of breweries present in each state.
noofbreweries <- aggregate(rep(1, length(breweriesdata$State)), by=list(breweriesdata$State), sum )
noofbreweries
```
```{r}
# Merge beerdata and breweriesdata by brewery id and stored in new data frame called m1 :
m1 <- merge(beerdata, breweriesdata, by.x = "Brewery_id" , by.y="Brew_ID")

#checking first 6 observations and last 6 observations of the merged data frame m1 :
head(m1)
tail(m1)
```
```{r}
#Total no of NA's and spaces in each column :
library(dplyr)
newm1 <- replace(m1,m1=="",NA)
m2 <- apply(newm1,2,function(x){sum(is.na(x))})
m2
```
```{r}
#To compute the median alcohol content and international bitterness unit for each state :
m3 <- aggregate(cbind(newm1$ABV,newm1$IBU)~State,FUN = median,newm1,na.rm=TRUE)
head(m3)
# we can plot the bar chart for better visualisation and to compare between alcohol content and international bitterness unit for each state:
ggplot(m3,aes(m3$State, y = m3$V1))+geom_bar(stat = "identity")+labs(x = "State" , y = "ABV") + ggtitle("ABV median per State")
ggplot(m3,aes(m3$State, y = m3$V2))+geom_bar(stat = "identity")+labs(x = "State" , y = "IBU") + ggtitle("IBU median per State")
# From the bar chart for median alcohol content and international bitterness unit by states indicates that most of the states are above 0.05 range and states with more alcohol content have more international bitterness unit of beer.
```


```{r}
#Finding state with maximum alcoholic beer and the most bitter beer:
m1[which.max(m1$ABV),]
m1[which.max(m1$IBU),]
#The state with the most bitter beer (IBU) is:OR with IBU=138
#The state with the maximum alcoholic beer (ABV) is:CO with ABU=0.128
```
```{r}
#summary statistics for ABV(Alcohol by volume) variable:
statistics <- summary(m1$ABV)
statistics
```
```{r}
# To draw scatterplot to find the relationship between the bitterness of the beer and its alcoholic content:
ggplot(beerdata,aes(x = ABV,y = IBU ))+geom_point(na.rm=TRUE)+geom_smooth(method=lm,se=FALSE, na.rm=TRUE)
# From the above scatterplot between ABV vs IBU,It is clearly seen that the if the alcohol content is increased the bitterness of beer also increased.so ABV and IBU have positive correlation even though there are some outliers in the data.
```

##Conclusion:
After the complete analysis of beers and breweries datasets,we can conclude that CO has the maximum alcohiolic beer with ABV=0.128, and OR has the most bitter beer with IBU=138.We were able to compute median alcohol content with summary statistics and international bitterness unit.For the better visualisation,we plot bar chart and scatterplot which also shows that there is a positive correlation between ABV and IBU.









